### 2013-12-25 docs/reports/finalreport/report.tex
finishing final report

\maketitle
\begin{abstract}
We did experiments on three datasets of different size and with different characteristics using Regression Algorithms. Four different algorithms where used for the experiment and for this four we did experiments varying their arguments data scaling and imputation techniques for missing data. In the report we first give an overview over the algorithms used, then we interpret the results of our experiments for each dataset and do a comparison of the different algorithms. In the end we try to compare the results of all datasets and draw conclusions.
\end{abstract}

@@

\input{introduction}
\newpage
\input{problem}
\newpage
\input{architecture}
\newpage
\input{design}
\newpage
\input{development}
\newpage
\input{future}
\newpage

>>>>

\maketitle
\begin{abstract}
The reports explains the efforts done by design and develop a translator
retrieval system. The system can be defined in domain of on-line translation. It aims to find an appropriate translator for a client and manages the process till the last step. Besides, by providing a translation memory system translators can apply their previous translated texts in their new ones. In the project, C\texttt{\#}.NET and MS SQL SERVER as main platform and Lucene.NET as text processor are used. It is designed based on DDD (Data Driven Design) model. Windows Azure is also selected as deployment environment.
\end{abstract}

@@

\input{introduction}
\newpage
\input{problem}
\newpage
\input{architecture}
\newpage
\input{design}
\newpage
\input{development}
\newpage
